Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-10-08 pdocs/thesis/epj-jcgt.tex
work on jcgt article

\teaser{
  \includegraphics[width=5cm]{figs/demolisher-done}
  \label{fig:teaser}
  \caption{Adding ductile breakable constraint to popular open source physics engine Box2D allows more realistic simulation of many scenarios.}
}

@@

\begin{abstract}
\small
This paper introduces simple and efficient method to simulate ductile fracture in existing 
impulse-based physics engines.
Method is based on technique of splitting bodies to multiple pieces and joining them with constraints.
Procedure to provide realistic parameters for constraints is described.
Procedure is based on body dimensions and material parameters.

@@

This paper follows idea of
allowing game designers to get desired behaviour without diving into details of structural engineering.
Idea was presented by Catto, \cite{ecsc}. Basic idea is that game designer selects spring frequency so that
integration is stable. Downside is that constraints will be quite soft. In out method game designers get new option
to use rigid-plastic constraints.

@@

During solution phase impulse is clamped so that it does not too big.
If clamping is activated additional processing is done at the beginnig of next step to update neutral position and
increment plasticity values.

@@

\paragraph{Car}

>>>>

\teaser{
  \includegraphics[width=5cm]{figs/CarAtRamp}
  \label{fig:teaser}
  \caption{Adding ductile breakable constraint to popular open source physics engine Box2D allows more realistic simulation of many scenarios. In picture above ramp is under elastic loading.}
}

@@

\begin{abstract}
\small
This paper introduces simple and efficient method to simulate ductile fracture in existing 
impulse-based physics engines.
Method is based on technique of splitting bodies to multiple pieces and joining them with constraints.
Procedure to provide realistic parameters for constraints is described.
Procedure may be based on body dimensions and material parameters or desired bahviour.

@@

This paper follows idea of
allowing game designers to get desired behaviour without diving into details of structural engineering.
Idea was presented by Catto, \cite{ecsc}. Basic idea is that game designer selects spring frequency so that
integration is stable. Downside is that constraints will be quite soft. In our method game designers get new option
to use rigid-plastic constraints.

@@

During solution phase impulse is clamped so that it does exceed predefined limit.
If clamping is activated additional processing is done at the beginnig of next step to update neutral position and
increment plasticity values.

@@

\paragraph{Car} 
Dynamic bodies are car (680 kg), wheels (50 kg for each axel), and ramp (2160 kg). 
Ramp is joined to fixed part with b2ElasticPlasticJoint having frequency of 1 Hz.
Maximum elastic rotation is set to 0.12 and maximum plastic rotation to 0.4.
With this configuration own weight or ramp uses about 13 \% of plastic capacity.
After first jump about 50 \% of  plastic capacity is used. Each additional jump uses about 
7 \% of plastic capacity.
